Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-09-30 response-reviewers-2.tex

{\bf Response to reviewers' comments}

We are very grateful to the reviewers for their kind comments. We have rewritten
the paper quite extensively, incorporating requested changes, but also
attempting to give another angle that makes this paper apart from what was
already published in this other one

Merelo, J.J. et al. (2022). Exploring the Role of Chatbots and Messaging
Applications in Higher Education: A Teacher's Perspective. In: Zaphiris, P.,
Ioannou, A. (eds) Learning and Collaboration Technologies. Novel Technological
Environments. HCII 2022. Lecture Notes in Computer Science, vol 13329. Springer,
Cham. https://doi.org/10.1007/978-3-031-05675-8\_16

This explains that, in some cases, conclusions have been extended or
reinterpreted over the ones published in that paper. Some of these extensive
changes have been noted in blue for their easy identification.
Additionally, we validated
the survey, as was also requested by the reviewers.

@@

    b. We have changed the title and moved the indicated paragraph. Thanks for
    the suggestion.

%%%%%% Rev 4

{\bf Reviewer \#4}: {\it First of all, this paper seems to be the main topic of 'Analysis from the teacher's perspective of chatbots and messaging platforms in class'.
It seems that simple survey results were analyzed and grouped.
It seems like a lot of effort was put into it, but I doubt whether it has any academic significance.
Why did you choose 4 questions? Is it appropriate for a chatbot and messaging platform if I just ask and group this? I am not sure.
Looking at the research results and conclusions, there are some contents that are difficult to see as valid because the evidence for the researcher's conclusions is so abrupt and abstract.}

The authors thank the reviewer for provinding useful feedback that has allowed
us to improve the quality of the paper.

Regarding the first issue (the lack of academic significance), we would like to
stress the importance of the topic of artificial intelligence tools bringing
changes in our lifestyle in the comming years. This study shares experiences
from the academic and educational point of view and analyses the results
obtained. Nonetheless, the Introduction (as well as other sections) has been
rewritten with the hope of addressing the academic significance in a clearer
way.

Regarding the validation of the methodology, there is a new subsection that
presents the validation procedure by means of an expert board which agrees with,
in general, agrees with the questions and answers we used in the survey.

### 2022-09-30 response-reviewers-2.tex

{\it 5.      Does the article distinguish clearly between opinion and empirical evidence? Yes
6.      Does the article contribute to a critical understanding of the issues? Yes
7.      Does the article alert readers to significant new developments in the subject area? Yes
8.      Does the article take into account relevant contemporary literature in the area? Yes.}

The authors want to thank the reviewer for evaluating positively those aspect of the paper.

% -> answer 9

{\it 9.      Does the article clearly reference citations and quotations using the APA 7th edition? Partly, some of the references do not follow APA 7th edition. For example, the following references don't follow APA 7th edition referencing style
     a.   O'Boyle, 2014. O'Boyle, N. (2014). Front row friendships: Relational dialectics and identity negotiations by mature students at univerty. Communication Education, 63(3):169-191
     b. Panah and Babar, 2020. Panah, E. and Babar, M. Y. (2020). A survey of WhatsApp as a tool for instructor-learner dialogue, learner-content dialogue, and learner-learner dialogue. International Journal of Educational and Pedagogical
 Sciences, 14(12):1198 - 1205.
     c. Perez et al., 2020. Perez, J. Q., Daradoumis, T., and Puig, J. M. M. (2020). Rediscovering the use of chatbots in education: A systematic literature review. Computer Applications in Engineering Education, 28(6):1549- 1565.
     d. Ranoliya et al., 2017. Ranoliya, B. R., Raghuwanshi, N., and Singh, S. (2017). Chatbot for university related faqs. In 2017 International Conference on Advances in Computing, Communications and Informatics (ICACCI), pages 1525-1530. IEEE.
     e. Roblyer et al., 2010. Roblyer, M., McDaniel, M., Webb, M., Herman, J., and Witty, J. V. (2010). Findings on facebook in higher education: A comparison of college faculty and student uses and perceptions of social networking sites. The Internet and Higher Education, 13(3):134 - 140.}

 We have used, as instructed by the template, the {\tt apalike} style in our
  LaTeX source, as well as used standard BiBTeX files downloaded from the
  publication itself. No tweaking has been mede on these, so I don't see what we
  can do about it, other than report a bug in the style to the authors.

We have been checking out the issue, and apparently the problem is that the 7th
edition is not well covered by the current LaTeX styles, which are stuck at the
6th edition. A pretty extensive change in tooling is needed, unfortunately,
including the style of bibliography citation and the tool used for doing
that. So while there's a path for doing this, we do not think it is something we
should devote our time in the current version of the paper, if the reviewer does
not mind. We will certainly do so as required by publication when (or if) this
paper is finally accepted

### 2022-09-30 edubots_surveys.Rnw
anonymize project

Given the potential benefits that chatbots could bring to the classroom, the
focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
and to create a learning community of educators in higher education institutions.
\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
\cite{abbas2021onlinechat}.}
\textcolor{blue}{The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding 
their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
how they can positively contribute to enhancing the learning process in higher education institutions.}

>>>>

Given the potential benefits that chatbots could bring to the classroom, the
focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
and to create a learning community of educators in higher education institutions.
\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
\cite{abbas2021onlinechat}.}
\textcolor{blue}{The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding 
their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
how they can positively contribute to enhancing the learning process in higher education institutions.}
